\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-10-27 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex

\tableofcontents
\vspace{1cm}
\newpage
\listoftables

@@

@@

\setcounter{table}{0}
\renewcommand{\thetable}{C.\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{C.\arabic{figure}}

@@

\begin{table}[htbp]
	\caption{Baseline and direct beta estimate 2005-2013}
	\begin{center}		
		\input{Comp_baseline_referee1_reshaped.tex}

@@

\begin{figure}[htbp]
	\caption{Baseline and direct beta estimate }
	\begin{center}
		\includegraphics[height=8cm]
		{../scatter_chronology_baseline_referee1.png}
	\end{center}
\end{figure}

@@

\begin{table}[htbp]
	\caption{Comparison 2005-2019, price per qy or price per kg}
	\begin{center}		
		\input{Comp_baseline_wgt_qy.tex}
	\end{center}
	\label{tab_comp_referee1_baseline}%
\end{table}%

\begin{figure}[htbp]
	\caption{Comparison 2005-2019, price per qy or price per kg}
	\begin{center}
	\includegraphics[height=8cm]
	{../scatter_chronology_non_séparé_wgt_non_séparé_qy.png}
	\end{center}
\end{figure}

@@

@@

\subsubsection{More on the Hummel's methodology}

This section complements Section 4 in the main paper, where we replicate the method adopted by \cite{hummels2007} on our database. Here, we report the unfitted measure of transport costs versus the ``pure'' transport costs series, i.e composition effects excluded
in percentage of the export price, as in \cite{hummels2007}. We also adopt Hummel's (2007) terminology, contrasting the ``expenditure/importe value'' (i.e, the unfitted serie) and the ``fitted ad-valorem rate'' (i.e, corresponding to the ``pure'' transport costs series, composition effects excluded). Unsurprisingly, this accords with his Figure 5 (for Air) and 6 (Vessel) for the comme period (until 2014).

\begin{figure}[htbp]
\caption{Characterizing the time trends: applying Hummel's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
{\small (A) Ad-valorem air freight} & {\small (B) Ad-valorem vessel freight}\\
\multicolumn{2}{c}{{\small In percent of the export price}} \\
\includegraphics[width=2.5in, height=1.8in]{figure5_comme_hummels.jpg}
& \includegraphics[width=2.5in,height=1.8in]{figure6_comme_hummels.jpg} \\
{\small (c) Ad-valorem air freight} & {\small (d) Ad-valorem vessel freight} \\
\end{tabular}
\end{center}
\end{figure}

\subsubsection{Composition effects: Primary vs. Manufacturing sector}
In this section, we refine the characterization of the evolution of international transport costs by distinguishing primary goods trade flows and and manufactured goods trade flows. The evolution in transport costs over time, by transport mode (overall transport costs and composition effects excluded) are reported in Figure \ref{fig:totalTC_compeffects_excl_manuf} for the manufacturing sector, and in Figure \ref{fig:totalTC_compeffects_excl_primary} for the primary goods. For easing comparison, we also report the results obtained on the whole range of trade flows (i.e., Figure 2 of the paper), in Figure \ref{fig:totalTC_compeffects_excl}.

>>>>

\tableofcontents
\vspace{1cm}
\newpage
\listoftables
\listoffigures

@@

\setcounter{table}{0}
\renewcommand{\thetable}{D.\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{D.\arabic{figure}}

@@

@@

\begin{table}[htbp]
	\caption{Baseline and direct $\beta$ estimate, 2005-2013}
	\begin{center}		
		\input{Comp_baseline_referee1_reshaped.tex}

@@

\begin{figure}[htbp]
	\caption{Baseline and direct $\beta$ estimate }
	\begin{center}
		\includegraphics[height=8cm]
		{../scatter_chronology_baseline_referee1.png}
	\end{center}
\end{figure}

@@

\begin{table}[htbp]
	\caption{Comparison 2005-2019, Price per quantity or Price per kg}
	\begin{center}		
		\input{Comp_baseline_wgt_qy.tex}
	\end{center}
	\label{tab_comp_referee1_baseline}%
\end{table}%

\begin{figure}[htbp]
	\caption{$\beta$ Estimate: Price per quantity or price per kg, 2005-2019}
	\begin{center}
\begin{tabular}{cc}
	\includegraphics[height=8cm]{../scatter_chronology_non_separe_wgt_non_separe_qy.png}\\
\multicolumn{2}{l}{{\footnotesize Notes: In both cases, estimation is run without imposing the separability assumption.}}
\end{tabular}
	\end{center}
\end{figure}

@@

\setcounter{table}{0}
\renewcommand{\thetable}{E.\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{E.\arabic{figure}}

@@

\subsubsection{More on the Hummels's methodology}

This section complements Section 4 in the main paper, where we replicate the method adopted by \cite{hummels2007} on our database. Here, we report the unfitted measure of transport costs versus the ``pure'' transport costs series, i.e composition effects excluded
in percentage of the export price, as in \cite{hummels2007}. The parallel with Hummels's (2007) terminology stands as follows: In Figure \ref{fig:comp_effects_as_in_Hummels}, the ``transport costs, excluding composition effects'' series refers to his ``fitted ad-valorem rate''; the ``transport costs'' series refers to his ``expenditure/import value''. Unsurprisingly, this accords with his Figure 5 (for Air) and 6 (Vessel) for the same period (until 2014).

\begin{figure}[htbp]
\caption{Characterizing the time trends: applying Hummels's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
{\small (A) Ad-valorem air freight} & {\small (B) Ad-valorem vessel freight}\\
\multicolumn{2}{c}{{\small In percent of the export price}} \\
\includegraphics[width=2.5in, height=1.8in]{figure5_comme_hummels.jpg}
& \includegraphics[width=2.5in,height=1.8in]{figure6_comme_hummels.jpg} \\
{\small (c) Ad-valorem air freight} & {\small (d) Ad-valorem vessel freight} \\
\end{tabular}
\end{center}
\end{figure}

\subsubsection{Composition effects: Primary vs. Manufacturing sector}

In this section, we refine the characterization of the evolution of international transport costs by distinguishing primary goods trade flows and and manufactured goods trade flows. The evolution in transport costs over time, by transport mode (overall transport costs and composition effects excluded) are reported in Figure \ref{fig:totalTC_compeffects_excl_manuf} for the manufacturing sector, and in Figure \ref{fig:totalTC_compeffects_excl_primary} for the primary goods. For easing comparison, we also report the results obtained on the whole range of trade flows (i.e., Figure 2 of the paper), in Figure \ref{fig:totalTC_compeffects_excl}.
